251 MA

### 2023-03-01 code/process.Rmd
add tier1model

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         log_ratio_ss = log(replication_N/target_N),
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
        open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
        is_within=case_when(
            within_between=="within" ~ 1,
            within_between=="mixed" ~ 1,
            within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
  predInt=as.numeric(predInt)) |> 
  select(target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
           stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
           predInt, p_orig, sub_rep)

@@

## tier 1 data
```{r}
data_tier1 <- z_data |> select(academic_year, sub_rep, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.)))

@@

## tier 2 data
```{r}
data_tier2 <- z_data |> select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.))) 
```

## tier 3 data
```{r}
data_tier3 <- z_data |> select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_target_d_calc, z_log_p, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |> filter(across(everything(), ~!is.na(.))) 
```

@@

```{r, eval=F}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        #family=gaussian(link='logit'), # runs
                        #family="cumulative", # runs on 1-5 data
                        # family="zero_one_inflated_beta", runs, 
                        # beta_binomial on 0-4 data
                        data=data_tier1,
                        #file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        iter=100,
                        control=list(adapt_delta=.99),
                        #backend="cmdstanr"
                        )
```

>>>>

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         log_ratio_ss = log(replication_N/target_N),
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
        open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
        is_within=case_when(
            within_between=="within" ~ 1,
            within_between=="mixed" ~ 1,
            within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
  predInt=as.numeric(predInt)) |> 
  select(include, target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
           stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
           predInt, p_orig, sub_rep)

@@

## tier 1 data
```{r}
data_tier1 <- z_data |> filter(include %in% c("stats", "exp", "pred_int")) |>
  mutate(sub_rep=sub_rep*4+1) |>  #remap to 1-5 scale
select(academic_year, sub_rep, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

@@

## tier 2 data
```{r}
data_tier2 <- z_data |> filter(include %in% c("stats", "pred_int")) |>
  select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) 
```

## tier 3 data
```{r}
data_tier3 <- z_data |>  filter(include %in% c("stats")) |>
  select(academic_year, sub_rep, 
                               p_orig, predInt,
                               z_target_d_calc, z_log_p, 
                               z_pub_year, subfield, open_data, open_mat, stanford, change_platform, z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) 
```

@@

```{r, eval=F}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```
